Fluent statistical computing interfaces for biological data analysis

### 2020-10-27 Rmd/06-conclusion.Rmd
update link in appendix

The **plyranges** package develops a suite of verbs for interacting
with genomic data as a *GRanges* object. Since its release on Bioconductor,
it  has been relatively  successful: it has been downloaded `r nice(plyranges_stats$no_downloads)` times from  `r nice(plyranges_stats$no_ip)` unique IP addresses. I have also had the privilege of teaching workshops on **plyranges**
at Bioconductor conferences which also led to the development of the 
**fluentGenomics** workflow package, outlined in chapter \@ref(ch:fluentGenomics). A broader impact of the work, has been the discussions around the
concepts of fluent interfaces and tidy data within the Bioconductor community,
which has led to several developments currently in place that are exploring
different approaches for fluent interfaces for other types of omics data.
The **plyranges** package is available to download from 
https://bioconductor.org/packages/release/bioc/html/plyranges.html and
the **fluentGenomics** workflow is available to download from 
https://bioconductor.org/packages/release/workflows/html/fluentGenomics.html.

>>>>

The **plyranges** package develops a suite of verbs for interacting
with genomic data as a *GRanges* object. Since its release on Bioconductor,
it  has been relatively  successful: it has been downloaded `r nice(plyranges_stats$no_downloads)` times from  `r nice(plyranges_stats$no_ip)` unique IP addresses. I have also had the privilege of teaching workshops on **plyranges**
at Bioconductor conferences which also led to the development of the 
**fluentGenomics** workflow package, outlined in chapter \@ref(ch:fluentGenomics). A broader impact of the work, has been the discussions around the
concepts of fluent interfaces and tidy data within the Bioconductor community,
which has led to several developments currently in place that are exploring
different approaches for fluent interfaces for other types of omics data.
The **plyranges** package is available to download from 
https://bioconductor.org/packages/plyranges and
the **fluentGenomics** workflow is available to download from 
https://bioconductor.org/packages/release/workflows/html/fluentGenomics.html.
